Approximation as Differentiation notes

### 2025-02-26 notes/sec/set-indexed-product.tex
First pass over set-indexed products.

$C$ \emph{has set-indexed products} if, for any set $I$ and any $I$-indexed family $X$ of objects of $C$,
there exists an object $\prod_{i \in I}X_i$ in $C$ and family of morphisms $\eval_i$ such that for any object
$Y$ of $C$ and any family of morphisms $\{f_i: Y \to X_i\}_{i \in I}$ in $C$, there exists a unique morphism
$\lambda f$ making the following diagram commute:

>>>>

$C$ \emph{has set-indexed products} if, for any set $I$ and any $I$-indexed family $X$ of objects of $C$,
there exists an object $\prod_{i \in I}X_i$ and family of morphisms $\eval_i$ in $C$ such that for any object
$Y$ of $C$ and any family of morphisms $\{f_i: Y \to X_i\}_{i \in I}$ in $C$, there exists a unique morphism
$\lambda f$ making the following diagram commute:
